Subject specific curves for time series forecasting of smart meter demand

### 2019-11-01 sscts-paper-1.Rmd
Fixed spelling of title
Remove unused scores script.

---
title: "Subject specific curves for times series forecasting of smart meter demand"
author: "Cameron Roach^[Corresponding author. E-mail address: cameron.roach@monash.edu (C. Roach).]"
fontsize: 11pt
papersize: a4
bibliography: ["library.bib", "packages.bib"]
biblio-style: authoryear-comp
subparagraph: true
toc: false
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{booktabs}
output:
  bookdown::pdf_document2:
  # MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: no
    number_sections: yes
    citation_package: biblatex
---

@@

library(tidyverse)
library(tsibble)
library(furrr)
library(lubridate)
library(stringr)
library(lme4)
# library(nlme)
library(splines)
library(forecast)
library(leaps)
source("R/load-data.R")
source("R/scores.R")
source("R/feature-selection.R")
source("R/test-models.R")
source("R/models-lme4.R")
source("R/plot-helpers.R")

>>>>

---
title: "Subject specific curves for time series forecasting of smart meter demand"
author: "Cameron Roach^[Corresponding author. E-mail address: cameron.roach@monash.edu (C. Roach).]"
fontsize: 11pt
papersize: a4
bibliography: ["library.bib", "packages.bib"]
biblio-style: authoryear-comp
subparagraph: true
toc: false
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{booktabs}
output:
  bookdown::pdf_document2:
  # MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: no
    number_sections: yes
    citation_package: biblatex
---

@@

library(tidyverse)
library(tsibble)
library(furrr)
library(lubridate)
library(stringr)
library(lme4)
# library(nlme)
library(splines)
library(forecast)
library(leaps)
source("R/load-data.R")
source("R/feature-selection.R")
source("R/test-models.R")
source("R/models-lme4.R")
source("R/plot-helpers.R")
